FIXME

### 2013-09-23 writeups/proposal/proposal.tex
foo
Former-commit-id: b8777ce7e056bd9c551392f0f23cb74fad518c13 [formerly 5f55ea69ee36ef944bf81d579621e80903e73c70]
Former-commit-id: 7a2d377bd9bea6cfa6ccab4d68d644e201e429b4

% FIXME: Use a different example figure
\begin{figure}[!htbp]
  \scalebox{.8}{\resizebox{\linewidth}{!}{\includegraphics{stackoverflowPostExample1-crop.pdf}}}
  \caption{Example post on stackoverflow.com}
  \label{figSOExample}
\end{figure}

An example StackOverflow post is included in Figure \ref{figSOExample}.
The site requires that for each post, the user must associate at least one tag with the post.
The author used 4 tags for this post: \emph{javascript}, \emph{firefox}, \emph{dom}, and \emph{svg}, and the average number of tags per post is around 3.

>>>>

% FIXME: Use vector-graphics for this figure 
\begin{figure}[!htbp]
  \scalebox{.8}{\resizebox{\linewidth}{!}{\includegraphics{stackoverflowPostExample1-crop.pdf}}}
  \caption{Example post on stackoverflow.com}
  \label{figSOExample}
\end{figure}

An example StackOverflow post is included in Figure \ref{figSOExample}.
The site requires that for each post, the user must associate at least one tag with the post.
The author used 4 tags for this post: \emph{javascript}, \emph{html}, \emph{internet-explorer}, and \emph{xhtml}, and the average number of tags per post is around 3.
